### 2018-05-17 Paper/method.tex
another comment on the algorithm ...

%%%%%%%%%%% Revised %%%%%%%%%%%
\bigskip
\begin{breakablealgorithm}
\renewcommand{\algorithmicrequire}{\textbf{Input:}}
\renewcommand{\algorithmicensure}{\textbf{Output:}}
  \caption{Parameter screening with DGSMs: A generalized approach.}
  \begin{algorithmic}[1]
\Require $\tau > 0$, $\tau_\text{screen} > 0$,
$s_\text{max}$, $\beta > 0$, $\{ \bm{\theta}_k \}_{k = 1}^{n_0}$, $\{ \bm{g}^k \}_{k=1}^{N_\text{total}}$. 
\Ensure $\mathcal{I}_\text{active}$, $\{ \bm{g}^k \}_{k=1}^{N_\text{total}}$, $N_\text{total}$. 
    \Procedure{Screening}{}
    %  \State Draw samples $\{ \bm{\theta}_k \}_{k = 1}^{n_1}$ 
     %  according to the probability density $\bm{f(\theta)}$.
     %   \State $N_\text{total} = N_\text{total} + n_1$.
      \State Compute $\bm{g}^k = \nabla_{\bm{\theta}}G(\bm\theta_k)$, 
             $k = 1, \ldots, n_1$.

      \State Compute 
      $\mu_{1, i} = \frac{1}{N_\text{total}} \sum_{k = 1}^{N_\text{total}} (g^k_i)^2$
      \State Compute $\nu_i = \widehat{\mathcal{C}_i\mu_{1,i}}$, for each $\theta_i$, 
             $i = 1, \ldots, \Np$. 
      \State Determine initial ranks: 
            let $\mathcal{R}^{old} = \{ \nu_{i_1}, \nu_{i_2}, \ldots, \nu_{i_\Np}\}$ such that 
\[
   \nu_{i_1} \geq \nu_{i_2} \geq \cdots \geq \nu_{i_\Np}. 
\]
      \State Set $s$ = 1.
      \State Set $\mathrm{done} = \mathrm{false}$.
      \While {$\mathrm{done} == \mathrm{false}$ \textbf{AND} $s \leq s_\text{max}$} 
        \State $s = s + 1$.
        \State Draw $n_s = \lceil \beta n_1 \rceil$ new samples 
                  $\bm{\theta}_k$, $k = n_{s-1} + 1, \ldots, n_{s-1} + n_s$
       \State $N_\text{total} = N_\text{total} + n_s$.
        \State Compute $\bm{g}^k = \nabla_{\bm{\theta}}G(\bm\theta_k)$,
             $k = n_{s-1}+1, \ldots, n_{s-1}+n_s$.

>>>>

%%%%%%%%%%% Revised %%%%%%%%%%%
\bigskip
\begin{breakablealgorithm}
\renewcommand{\algorithmicrequire}{\textbf{Input:}}
\renewcommand{\algorithmicensure}{\textbf{Output:}}
  \caption{Parameter screening with DGSMs: A generalized approach.}
  \begin{algorithmic}[1]
\Require $\tau > 0$, $\tau_\text{screen} > 0$,
$s_\text{max} \geq 1$, $\beta > 0$, $\{ \bm{\theta}_k \}_{k = 1}^{n_0}$, $\{ \bm{g}^k \}_{k=1}^{N_\text{total}}$. 
\Ensure $\mathcal{I}_\text{active}$, $\{ \bm{g}^k \}_{k=1}^{N_\text{total}}$, $N_\text{total}$. 
    \Procedure{Screening}{}
    %  \State Draw samples $\{ \bm{\theta}_k \}_{k = 1}^{n_1}$ 
     %  according to the probability density $\bm{f(\theta)}$.
     %   \State $N_\text{total} = N_\text{total} + n_1$.
      \State Compute $\bm{g}^k = \nabla_{\bm{\theta}}G(\bm\theta_k)$, 
             $k = 1, \ldots, n_1$. 
\alennote{Should we have $n_1 = n_0$? Also, there is an issue with this 
algorithm: when you call this first time according to the flow diagram, you will
not actually have the gradients $\bm{g}^k$, $k = 1, \ldots, N_\text{total}$;
moreover, we need to explicitly augment the gradient samples with the ones 
passed to the method. Moreover, I think the step $N_\text{total} = N_\text{total} + n_0$
should be in the body of this algorithm, as opposed to where it is in the flow 
diagram.}
      \State Compute 
      $\mu_{1, i} = \frac{1}{N_\text{total}} \sum_{k = 1}^{N_\text{total}} (g^k_i)^2$
      \State Compute $\nu_i = \widehat{\mathcal{C}_i\mu_{1,i}}$, for each $\theta_i$, 
             $i = 1, \ldots, \Np$. 
      \State Determine initial ranks: 
            let $\mathcal{R}^{old} = \{ \nu_{i_1}, \nu_{i_2}, \ldots, \nu_{i_\Np}\}$ such that 
\[
   \nu_{i_1} \geq \nu_{i_2} \geq \cdots \geq \nu_{i_\Np}. 
\]
      \State Set $s$ = 1.
      \State Set $\mathrm{done} = \mathrm{false}$.
      \While {$\mathrm{done} == \mathrm{false}$ \textbf{AND} $s \leq s_\text{max}$} 
        \State $s = s + 1$.
        \State Draw $n_s = \lceil \beta n_1 \rceil$ new samples 
                  $\bm{\theta}_k$, $k = n_{s-1} + 1, \ldots, n_{s-1} + n_s$
       \State $N_\text{total} = N_\text{total} + n_s$.
        \State Compute $\bm{g}^k = \nabla_{\bm{\theta}}G(\bm\theta_k)$,
             $k = n_{s-1}+1, \ldots, n_{s-1}+n_s$.
